---
title: "Quarto Programmatically Customized Emails (with Connect)"
author: "Lisa Anders"
format: email
---

Make the magic happen: <https://docs.posit.co/connect/user/quarto/#email-customization> 

> Email customization requires Quarto 1.4.

## How to run this 

1. First `re-render`refresh report` (this will update the variant). 

2. Then `email report` (this will use the newly selected variant).

3. Because the variant is randomly selected, the same variant might be used. I'm okay with repeat meals! 


## Email notifications: Generate email contents

Modify the yaml to change the output format (note that a specific quarto version or most recent is required): 

```
format: email
```

Add a section to define the email content. Files can be attached, calculation outputs can be included, and this can even be wrapped in a conditional statement to only send on certain conditions: 

Randomly select a condition to demonstrate different conditions: 

```{r}
variant <- sample(1:3, 1)
```

Match the email to the variant selected: 

```{r}
#| output: asis
cat(
  "---",
  paste0("is_email_variant_",variant,": true"),
  "---",
  sep = "\n"
)
```

::: {.email}

::: {.content-visible when-meta="is_email_variant_1"}

<!-- email case 1 -->

Remember to pick up groceries on your way home. Tonight is "breakfast for dinner" and we're having French Toast!

* Bread
* Eggs
* Butter
* Milk

This email was sent from Quarto! With conditional output for condition `r variant`

```{r}
#| echo: false

cat(paste0("Generated on: ", Sys.Date()))
```

::: {.subject}
Dinner plans: "Breakfast for Dinner"
:::

:::

::: {.content-visible when-meta="is_email_variant_2"}

<!-- email case 2 -->

Remember to pick up groceries on your way home. Tonight is "Tex-mex" and we're having tacos!

* Onions
* Bell peppers
* Fajita
* Tortillas
* Lime
* Avocado

This email was sent from Quarto! With conditional output for condition `r variant`

```{r}
#| echo: false

cat(paste0("Generated on: ", Sys.Date()))
```

::: {.subject}
Dinner plans: Tex-mex
:::

:::

::: {.content-visible when-meta="is_email_variant_3"}

<!-- email case 3 -->

Remember to pick up groceries on your way home. Tonight we're having stir fry!

* Snap peas
* Noodles
* Tofu
* Soy Sauce
* Rice

This email was sent from Quarto! With conditional output for randomly selected variable: `r variant`

```{r}
#| echo: false

cat(paste0("Generated on: ", Sys.Date()))
```

::: {.subject}
Dinner plans: Stir fry
:::

:::

:::

### Logging

Case: `r variant`

Report run: `r Sys.time()`

## Send email

::: {.email-scheduled}
TRUE
:::

