---
title: "Quarto Conditional Emails (with Connect)"
author: "Lisa Anders"
format: email
---

## Email notifications: Alert when a new blog post has been released

```{r}
library(tidyRSS)
library(dplyr)
library(lubridate)

# Test your rss generator using this URL for the contents of the R Journal
rss_url <- "https://posit.co/feed/"
```

```{r}
rss <- tidyfeed(rss_url)
```

Check if the date for a published blog post happened in the last 24 hours. This can be changed with using different scheduling options when published to Connect and changing the lookback time. 

```{r}
rss_new <- rss %>% select(-feed_category, -item_category) %>% filter(item_pub_date >= (now() - days(1)))
```

Set up logic to check if conditions have been met to send the email, else stop rendering the document. 

```{r}
if (nrow(rss_new > 0)) {
  # continue
  print("New posts found")
} else {
  stop("No new blog posts, stopping")
}
```



Send an email. 

::: {.email}

::: {.subject}
Alert: There is a new Posit blog post!
:::

Check out the new blog post, **`{r} paste(rss_new$item_title, sep = ", ")`**, [here](`{r} paste(rss_new$item_link, sep = ", ")`)

:::


## Implementation notes

References: 

- <https://docs.posit.co/connect/user/quarto/index.html#email-customization> 
- <https://quarto.org/docs/authoring/conditional.html> 
- <https://github.com/rich-iannone/quarto-email/issues/9> 

### RSS feed details

Goal: Using the RSS feed from [the published sample blog](https://colorado.posit.co/rsc/connect/#/apps/1561d39e-977a-4e5c-9e73-857860b3d076/access) this quarto document will send an email when a new blog has been published. 

The [quarto RSS feed option](https://quarto.org/docs/websites/website-blog.html#rss-feed) will need to be enabled on the site that will be tracked. We can then use [tidyrss](https://robertmyles.github.io/tidyRSS/) to read the rss file back. 

This is using an example that was [deployed to Posit Connect](https://quarto.org/docs/publishing/rstudio-connect.html#publish-command) for the email generation with the [Connect Email Generation feature](https://quarto.org/docs/prerelease/1.4/email.html). 

Limitations: 

- This implementation currently doesn't have handling for authentication and only works with RSS feeds for public blogs or blogs posted to Connect that have been published **anyone, no login required**. 
- What happens if the scheduling service is interrupted for some reason? Right now the lookback is still just for the last 1 day. Other options could be to `pin` the xml and use that to compare to what was available the last time it ran, or use `connectapi` to check when last it successfully ran and use that to generate a timeframe. 
- Email customization requires Quarto 1.4.